### 2022-11-25 Manuscripts/model_descriptions/jern-kemp-conjugate/jern-kemp-conjugate.tex
STILL HYPHENS AAHHHHHHHHHHHH

\section*{Conjugate Implementation of the Jern \& Kemp (2013) Model with Representativeness}

The representativeness model is very similar to the Jern \& Kemp (2013)
hierarchical Bayesian model. The essential difference here is the ultimate
formulation of response probabilities. Where in the original hierarchical
Bayesian model the exemplars are drawn from Gaussian distributions, in the
representativeness model each exemplar is drawn in proportion to the exemplar's
representativeness. The representativeness of an exemplar is defined by
Tenenbaum and Griffiths (2012) as the relative evidence that is provided by the
exemplar $x$ for a given hypothesis $h$ compared to all other hypotheses $h'$:

\begin{equation}
  R(x,h) = \log \dfrac{p(x|h)}{\sum_{h'\neq h}{p(x|h')p(h')}}
\label{representativeness}
\end{equation}

For simplicity, and consistency with the original hierarchical Bayesian model,
we define $h_{C}$ as a multivariate normal distribution for a particular
category $C$ parameterised by $\mu_C$ and $\Sigma_C$. For completeness, this
document will repeat some information from the hierarchical Bayesian model
document and describee how we compute these variables.

@@

As mentioned earlier, this is the point where the representativeness model
diverges from the hierarchical Bayesian model. Specifically, the probability of
generating exemplar $x$ is proportional to its representativeness:

\begin{equation}
  p(x) \propto R(x,h) ,
\end{equation}
where $h$ is a multivariate normal distribution parameterised by $\mu_{C}$ and
$\Sigma_{C}$.

In practice, $p(x)$ is computed by first obtaining the representativeness of
every possible generation candidate $x_i$. The end probability is a
normalization of these values:

\begin{equation}
  p(x) = \dfrac
    {\exp( \theta \cdot R(x,h))}
    {\sum_i \exp( \theta \cdot R(x_i,h_i))} 
\end{equation}
\
where $\theta$ is a response determinism parameter.

>>>>

\section*{Conjugate Implementation of the Jern \& Kemp (2013) Model}

Category members ($x_A$ or $x_B$; more generally written as $x_C$) are assumed to have been generated using an underlying category distribution (specifically, multivariate normal):
\
\begin{equation}
  x_C \sim Normal(\mu_{C}, \Sigma_{C})
\end{equation}
\
$p(y | x_C)$ is proportional to the candidate's density under the target category's distribution. Thus, obtaining the category distribution parameters $(\mu_{C}, \Sigma_{C})$ is key for generation. This document describes how we compute these variables in a conjugate model.

@@

$x$ are assumed to be drawn from a the distribution given by $Normal(\mu_{C}, \Sigma_{C})$. Thus,

\begin{equation}
  p(y) \propto Normal(y; \mu_{C}, \Sigma_{C})
\end{equation}

In practice, $p(y)$ is computed by first obtaining the relative density of every possible generation candidate $y_i$ under the category distribution. The end probability is a normalization of these values:

\begin{equation}
  p(x) = \dfrac
    {exp( \theta Normal(y ; \mu_{C}, \Sigma_{C}))}
    {\sum_i exp( \theta Normal(y_i ; \mu_{C}, \Sigma_{C}))} 
\end{equation}
\
where $\theta$ is a response determinism parameter.

### 2022-11-25 Manuscripts/model_descriptions/packer/packer_new.tex
STILL HYPHENS AAHHHHHHHHHHHH

>>>>

Where $f(x_j)$ is a function specifying each stored example's degree of
contribution toward generation. Although $f(x_j)$ may be set arbitrarily, in
PACKER it is set according to class assignment. For known members of the target
category, $f(x_j) = \theta_t$. For members of contrast categories, $f(x_j) =
-\theta_c$. $\theta_t$ and $\theta_c$ are free parameters ($0 \leq \theta_c, \theta_t$)
respectively controlling the within-class similarity and between-class
dissimilarity: $\theta_t > 0, \theta_c = 0$ produces exclusive consideration of same-category
members, and $\theta_t = 0, \theta_c > 0$ produces exclusive consideration of opposite-category
members. When both $\theta_t = \theta_c$, the similarity to contrast categories is
effectively subtracted from the similarity to the target category.

\begin{equation} p(y) = \dfrac { \exp \left \{ \cdot a \left( y, x
\right) \right \} } { \sum_i{ \exp \left \{  \cdot a \left( y_i, x \right)
\right\} } }
\label{eq:packer-choice}
\end{equation}

\subsection{An Older Version of PACKER: Didn't make it to any of the revisions, but was briefly considered}
This model assumes that people represent categories as exemplars in a
multidimensional space, and that generation is constrained by both similarity to
members of the category being generated \textit{and} dissimilarity to members of
other categories. The model assumes people generate categories that are
dissimilar to known categories and have strong within-class similarity.
